Empirical Evaluation of eval in R

### 2020-11-26 inst/analysis/environments.Rmd

```{r loading_fst}
eval_calls <- read_fst("/var/lib/R/project-evalR/run/package-evals-traced-test/calls.fst") %>%
  as_tibble() %>%
  deduplicate() %>% 
  add_types() %>%
  add_eval_source(eval_calls_raw) %>% add_eval_source_type()
```

>>>>

```{r loading_fst}
eval_calls <- read_fst("/var/lib/R/project-evalR/run/package-evals-traced-test/calls.fst") %>%
  as_tibble() %>%
  deduplicate()

eval_calls <-   add_eval_source(eval_calls) %>% add_eval_source_type()
```
